---
title: "Distributed ARIMA - Implementation with Pyspark"

abstract: "The following paper contains a brief introduction to ARIMA models and the elaboration of a DARIMA model based on the paper of Wang et. al. Distributed ARIMA models for ultra-long time series. The goal of this work is an implementation similar to the above mentioned authors with the framework Pyspark. The paper is written in the module Data Analysis in Big-Data and aims at highlighting the advantages of distributed computing."

keywords: "DARIMA, Time-Series, Distributed computing, Forecasting"

course: Datenanalyse in Big Data (Prof. Dr. Buchwitz)
supervisor: Prof. Dr. Buchwitz
city: Meschede

# List of Authors
author:
- familyname: Hoheisel
  othernames: Jonas
  address: "MatNr: 30321814"
  qualifications: "Data Science (2. Semester)"
  email: jonashoheisel45@googlemail.com
  correspondingauthor: true
  


# Language Options
german: false # German Dummy Text
lang: en-gb   # Text Language: en-gb, en-us, de-de

# Indexes
toc: true     # Table of Contents
lot: false    # List of Tables
lof: false    # List of Figures

# Output Options
bibliography: references.bib
biblio-style: authoryear-comp
blind: false
cover: true
checklist: true
output:
  fhswf::seminarpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: no
    number_sections: yes
    citation_package: biblatex
knit: fhswf::render_seminarpaper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=FALSE, messages=FALSE, warning=FALSE, 
                      attr.source='.numberLines', singlespacing = TRUE)
fhswf::fhswf_hooks()

# Load Packages
library(fhswf)
library(ggplot2)
library(dplyr)
library(tidyverse)
```

# Abstract
# Introduction
# ARIMA and distributed computing
# Map
# Reduce
# Implementation Google Cloud
# Forecast
## Point forecast
## Prediction intervals
# Evaluation
Evaluating the accuracy and reliability of forecasting models is a critical aspect of decision making in various fields varrieng from finance, engineering to epdemiology. Two commonly used metrics for assesing forecast performance are the Mean absolute Scaled Error (MASE) and the Mean Scaled Interval Score (MSIS). These metrics allow to evaluate the quality of forecasts and to compare it with other models by a uniticized value.

On the one hand, the MASE provides a measure of forecast that is robust to the scale and distribution of the data, making it applicable for comparing forecasts across different contexts. On the ohter hand, the MSIS assesses the quality of prediction intervals, quantifying the coverage of uncertainty inherent in forecasts. Combined, both values MASE and MSIS, they contribute to a comprehensive evaluation of point forecasts and prediction intervals.

In the following both values and equations are briefly introduced and applied to the determined forecasts based on the Nemassboost dataset. The goal is to evaluate the quality of the solution in comparison to the paper of Wang et. al. (@Wang2022).

## MASE - Mean absolute scaled error
In evaluating the accuracy of point forecasts, the mean absolute scaled error (MASE) can be chosen as metric. The error measure is first introduced by Hyndman and Köhler in 2006  20. 

\begin{equation} MASE = \frac{\frac{1}{H}\ \ \sum_{t=T+1}^{T+H}{\ \ \left|y_t-{\hat{y}}_{t|T}\right|}}{\frac{1}{T-m}\ \sum_{t=m+1}^{T}{\ \ \left|y_t-y_{t-m}\right|}} \end{equation}



## MSIS - Mean scaled intervals core

\begin{equation} 
MSIS = \frac{\frac{1}{H}\sum_{t=T+1}^{T+H}(U_{t|T}-L_{t|T}) + \frac{2}{\alpha}(L_{t|T}-y_t) \mathbf{1}\{y_t<L_{t|T}\} + \frac{2}{\alpha}(y_t - U_{t|T}) \mathbf{1}\{y_t > U_{t|T}\}}{\frac{1}{T-m}\sum_{t=m+1}^T |y_t - y_{t-m}|}
\end{equation}


## performance - Pyspark (Laufzeit)
# Discussion
# Summary


\newpage
# Appendix 

# Technical Appendix {-}

```{r, echo = TRUE}
Sys.time()
sessionInfo()
```

